---
title: "Play Time"
---
The goal is to assess how child friendly (or not) my collection is. If you don't care about the programming and stuff, just [skip ahead](#the-result).

```{r message=FALSE, echo=FALSE, error=FALSE, warning=FALSE}
# load libraries
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
```

## The process
The process is split in different parts:  
* Loading the data  
* Cleaning up

### Loading the data
To analyse all age ratings through all the libraries, we first load the existing `.csv` files with the data from Plex. We then combine them into one giant data frame.
```{r warning=FALSE, message=FALSE, error=FALSE}
all_movie_libraries <- list.files(path = "data", pattern = "*.csv", full.names = TRUE) %>%
                              lapply(read.csv) %>%
                              lapply(\(x) mutate(x, across(Audience.Rating, as.double))) %>%
                              bind_rows()
```


```{r warning=FALSE, message=FALSE, error=FALSE}
all_movie_libraries <- all_movie_libraries %>%
                                separate(Duration, c('play_time_hours', 'play_time_minutes', 'play_time_seconds'), ':') %>%
                                mutate(play_time_hours = as.numeric(play_time_hours), play_time_minutes = as.numeric(play_time_minutes), play_time_seconds = as.numeric(play_time_seconds)) %>%
                                mutate(play_time_single_in_minutes = ceiling(play_time_hours*60 + play_time_minutes + play_time_seconds/60)) %>%
                                select(title = Title,view_count = View.Count, play_time_single_in_minutes)
                                
head(all_movie_libraries)
```


```{r warning=FALSE, message=FALSE, error=FALSE, echo=FALSE}
row_count_before_filtering = nrow(all_movie_libraries)
```

```{r warning=FALSE, message=FALSE, error=FALSE}
all_movie_libraries = all_movie_libraries %>%
                          filter(view_count != 'N/A')
```
With this we reduced the rows in our data frame from `r row_count_before_filtering` to `r nrow(all_movie_libraries)`.

```{r warning=FALSE, message=FALSE, error=FALSE}
all_movie_libraries <- all_movie_libraries %>%
                        mutate(view_count = as.numeric(view_count)) %>%
                        mutate(play_time_total_in_minutes = play_time_single_in_minutes * view_count) %>%
                        select(title, play_time_total_in_minutes)

head(all_movie_libraries)
```

```{r warning=FALSE, message=FALSE, error=FALSE}
all_movie_libraries <- all_movie_libraries %>%
                        arrange(desc(play_time_total_in_minutes)) %>%
                        head(10)

all_movie_libraries %>% 
  ggplot(aes(x=title, y=play_time_total_in_minutes, color=play_time_total_in_minutes)) +
    geom_bar(stat="identity", fill="white") +
    scale_x_discrete(guide = guide_axis(angle = 90)) +
    geom_text(aes(label=play_time_total_in_minutes), position = position_dodge(1.9), size=3.5, vjust=1.6) +
    labs(title = 'My most watched movies by time spent watching', y = 'Time watched in minutes', x = 'Movie Titles') +
    theme_classic()
```